\bf Title here

### 2022-11-17 project/PaperTemplate/paper.Rmd
Finished percentile method section.

The standard confidence interval is built based on the assumption that the distribution from which we are sampling is Normal. This means that for an unknown distribution, the standard confidence interval could present an unmeaningful range. However, the same process can be used with bootstrap sampling to form the bootstrap percentile method.

>>>>

The standard confidence interval is built based on the assumption that the distribution from which we are sampling is Normal. This means that for an unknown distribution, the standard confidence interval could present an incorrect range. However, the same process can be used with bootstrap sampling to form the bootstrap percentile method. This means that an approximate bootstrap confidence interval will be created in the same automatic way that the standard confidence interval was created.

The percentile method interval is defined as the interval between the $100 * \alpha$ and the $100(1 - \alpha)$ percentiles of the bootstrap distribution of $\hat{\theta}$. That is, the $(1 - 2\alpha)$ coverage interval can be defined as $$[\hat{\theta}^*_\alpha,\hat{\theta}^*_{1-\alpha}].$$ In the case that the bootstrap distribution of $\hat{\theta}^* \sim N(\hat{\theta}, \hat{\sigma}^2)$, the corresponding percentile interval would be equivalent to the standard interval. However, this is not usually the case. When the bootstrap distribution is non-normal, we can suppose that there exists, for all $\theta$, $$\hat{\phi} \sim N(\phi, \tau^2),$$ for some monotone transformation $\hat{\phi} = g(\hat{\theta}), \phi = g(\theta)$, and $\tau$ is a constant. In other words, this transformation perfectly normalizes the distribution of $\hat{\theta}$. This transformation invariant can be applied to the bootstrap replications such that $$\hat{\phi}^{*b} = g\left( \hat{\theta}^{*b}\right ) \text{ for } b = 1,2,\dots, B.$$ The corresponding percentiles of the distribution transform similarly, $\hat{\phi}^*_\alpha = g \left ( \hat{\theta}^*_\alpha \right )$. Or we can say that the $(1 - 2\alpha)$ percentile interval is $\hat{\phi} \pm \tau z_\alpha$ which can also be represented as  $[\hat{\phi}^*_\alpha,\hat{\phi}^*_{1-\alpha}]$. This means that the interval on the $\theta$ scale can be defined as $$\hat{\theta}^*_\alpha = g^{-1}(\hat{\phi} \pm \tau z_\alpha).$$ Or $\left [ g^{-1}(\hat{\phi} \pm \tau z_{1-\alpha}), g^{-1}(\hat{\phi} \pm \tau z_\alpha) \right ]$. Therefore, the percentile method produces a correct interval for $\phi$ and due to the transformation invariance, also produces a correct percentile interval for $\theta$. This method assumes the existence of some monotone normalizing mapping $\hat{\phi} = g(\hat{\theta}), \phi = g(\theta)$ and relies on that to create a correct interval. Since the process is automatic, we do not need to know the transformation itself, only that it exists. However, in some cases, no monotone normalizing mapping will exist.

### 2022-11-17 project/PaperTemplate/paper.tex
Finished percentile method section.

The standard confidence interval is built based on the assumption that
the distribution from which we are sampling is Normal. This means that
for an unknown distribution, the standard confidence interval could
present an unmeaningful range. However, the same process can be used
with bootstrap sampling to form the bootstrap percentile method.

>>>>

The standard confidence interval is built based on the assumption that
the distribution from which we are sampling is Normal. This means that
for an unknown distribution, the standard confidence interval could
present an incorrect range. However, the same process can be used with
bootstrap sampling to form the bootstrap percentile method. This means
that an approximate bootstrap confidence interval will be created in the
same automatic way that the standard confidence interval was created.

The percentile method interval is defined as the interval between the
\(100 * \alpha\) and the \(100(1 - \alpha)\) percentiles of the
bootstrap distribution of \(\hat{\theta}\). That is, the
\((1 - 2\alpha)\) coverage interval can be defined as
\[[\hat{\theta}^*_\alpha,\hat{\theta}^*_{1-\alpha}].\] In the case that
the bootstrap distribution of
\(\hat{\theta}^* \sim N(\hat{\theta}, \hat{\sigma}^2)\), the
corresponding percentile interval would be equivalent to the standard
interval. However, this is not usually the case. When the bootstrap
distribution is non-normal, we can suppose that there exists, for all
\(\theta\), \[\hat{\phi} \sim N(\phi, \tau^2),\] for some monotone
transformation \(\hat{\phi} = g(\hat{\theta}), \phi = g(\theta)\), and
\(\tau\) is a constant. In other words, this transformation perfectly
normalizes the distribution of \(\hat{\theta}\). This transformation
invariant can be applied to the bootstrap replications such that
\[\hat{\phi}^{*b} = g\left( \hat{\theta}^{*b}\right ) \text{ for } b = 1,2,\dots, B.\]
The corresponding percentiles of the distribution transform similarly,
\(\hat{\phi}^*_\alpha = g \left ( \hat{\theta}^*_\alpha \right )\). Or
we can say that the \((1 - 2\alpha)\) percentile interval is
\(\hat{\phi} \pm \tau z_\alpha\) which can also be represented as
\([\hat{\phi}^*_\alpha,\hat{\phi}^*_{1-\alpha}]\). This means that the
interval on the \(\theta\) scale can be defined as
\[\hat{\theta}^*_\alpha = g^{-1}(\hat{\phi} \pm \tau z_\alpha).\] Or
\(\left [ g^{-1}(\hat{\phi} \pm \tau z_{1-\alpha}), g^{-1}(\hat{\phi} \pm \tau z_\alpha) \right ]\).
Therefore, the percentile method produces a correct interval for
\(\phi\) and due to the transformation invariance, also produces a
correct percentile interval for \(\theta\). This method assumes the
existence of some monotone normalizing mapping
\(\hat{\phi} = g(\hat{\theta}), \phi = g(\theta)\) and relies on that to
create a correct interval. Since the process is automatic, we do not
need to know the transformation itself, only that it exists. However, in
some cases, no monotone normalizing mapping will exist.
